---
title: "ussie"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ussie}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ussie)
library(dplyr)
```

Ussie let's you work with English football league data making a more standardized tibble for each country.

Typically you show how to use the function here:
```{r}
spain <- uss_make_matches(engsoccerdata::spain, "Spain")
glimpse(spain)
```

Let's try and use the "get_matches.R" function. This is a nice function becuase it cleans up the naming conventions that we struggled by writing them out through yesterday. 

It also helps because you can enter any case string and it will return a capitalized first letter in the country column
```{r}
italy_matches <- 
  uss_get_matches("italy")

glimpse(ital_matches)

```

We can add filtering conditions!
```{r uss_get_matches_filter}
uss_get_matches("england", season == 1966)
```

